Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-10-21 manuscript_latex/manuscript.tex
Add acknowledgements.
Fixed spelling error.

\caption{Estimated marginal effect of learners, normalisation and transformation methods on ranked model performance scores in 18560 machine learning experiments on 232 datasets. The top-left panel shows the marginal effect of learners, i.e. random forests and generalised linear models (GLM). Random forests outperform GLM models for all task difficulties. The top-right panel shows the marginal effect of feature normalisation methods, i.e. no normalisation and z-standardisation. z-standardisation is generally beneficial, but the estimated effect is neglible. The bottom panel shows the marginal effects of different transformation methods, split by learner and normalisation method. There is no consistent behaviour, and estimated effects are neglible. Note that the ranges of the $x$-axes of the three main panels differ. ECNT: empirical central normality test.}\label{fig:marginal-effect-plot}
\end{figure}

@@

>>>>

\caption{Estimated marginal effect of learners, normalisation and transformation methods on ranked model performance scores in 18560 machine learning experiments on 232 datasets. The top-left panel shows the marginal effect of learners, i.e. random forests and generalised linear models (GLM). Random forests outperform GLM models for all task difficulties. The top-right panel shows the marginal effect of feature normalisation methods, i.e. no normalisation and z-standardisation. z-standardisation is generally beneficial, but the estimated effect is negligible. The bottom panel shows the marginal effects of different transformation methods, split by learner and normalisation method. There is no consistent behaviour, and estimated effects are negligible. Note that the ranges of the $x$-axes of the three main panels differ. ECNT: empirical central normality test.}\label{fig:marginal-effect-plot}
\end{figure}

@@

\section{Acknowledgements}\label{sec:acknowledgments}

This research did not receive any specific grant from funding agencies in the public, commercial, or not-for-profit sectors.
